{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion}

### 2017-01-06 proposal/410.tex
landlside for grabing

TODO

>>>>

Beginning in 2017, I will recruit 15-410 Teaching Assistants (TAs) for my user study rather than students.
The modified user study will evaluate Landslide as a grading tool,
alternative to the ``Fritz'' stress-testing infrastructure which 15-410 currently employs,
and possibly substituting as well for the human process of reading student code looking for concurrency bugs by hand.
The intent is not for Landslide to ultimately replace 15-410's manual grading process,
but rather to demonstrate that comparably-rigorous grading could be deployed automatedly at other schools wishing to adopt the 15-410 curriculum.

I will pursue the following evaluation questions:

\begin{itemize}
	\item Provided appropriate test cases, can Landslide find the most common ``deep'' concurrency bugs in student submissions?
	\item How does Landslide's bug-finding compare to that of Fritz, the class's stress tester?
	\item How does Landslide's bug-finding compare to that of TAs grading by hand?
\end{itemize}

Finally, I will conclude this chapter in the thesis by discussing how future work could adapt Pebbles's interface to support fully-automatic model checking without compromising the educational value of P3.
